Preprocessing

### 2023-08-10 docs/presentation/preprocess.Rmd
viz: cast 5 levels to 4
viz: Q5 changes

clouds_q6 <- append(clouds_q6_q3, clouds_q6_q4)
clouds_q6$Everyone <- clouds$Q6
# saveRDS(clouds_q6, file = "data/clouds_q6.rds")
```

@@

## Bar charts
Cast 5 levels to 4
```{r eval=FALSE, include=FALSE}
analysis %<>%
  mutate(
    across(
      all_of(five_level_cols),
      ~ case_when(
        . == "Never" ~ "Not at all",
        . == "Rarely" ~ "Very little",
        . == "Some of the time" ~ "Somewhat",
        . %in% c("Most of the time", "Always") ~ "To a great extent"
      )
    )
  )
```

@@

Q7 (many parts)

Q13 (percentages)

## Likert charts
Q8

Q9 (maybe)

Q11
Q12

Q14

Q17

## Bar plot
Or something simple
Include animations

Q16

## Demographics

>>>>

clouds_q6 <- append(clouds_q6_q3, clouds_q6_q4)
clouds_q6$Everyone <- clouds$Q6
saveRDS(clouds_q6, file = "data/clouds_q6.rds")
```

```{r q10 cloud}
clouds_q10_q3 <- map(
  subfields, ~ analysis %>%
    filter(Q3_recoded == .x) %>%
    column_to_cloud("Q10", data = .)
) %>%
  set_names(subfields)

clouds_q10_q4 <- map(
  types, ~ analysis %>%
    filter(Q4 == .x) %>%
    column_to_cloud("Q10", data = .)
) %>%
  set_names(types)

clouds_q10 <- append(clouds_q10_q3, clouds_q10_q4)
clouds_q10$Everyone <- clouds$Q10
# saveRDS(clouds_q10, file = "data/clouds_q10.rds")
```

@@

## Bar charts
Cast 5 levels to 4
```{r}
analysis %<>%
  mutate(
    across(
      all_of(five_level_cols),
      ~ case_when(
        . == "Never" ~ "Not at all",
        . == "Rarely" ~ "Very little",
        . == "Some of the time" ~ "Somewhat",
        . %in% c("Most of the time", "Always") ~ "To a great extent"
      )
    )
  )
```

@@

Rename Q6 labels
```{r}
analysis %<>%
  mutate(label = case_match(
    label,
    "Omit" ~ NA,
    "Standard" ~ "Assess Prior Work",
    "Experiment" ~ "Repeatable Experiments",
    "Data Collection" ~ "Data Collection",
    "Transparency/Extension" ~ "Transparency/Extension"
  ))
```
